Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - WiP}}

### 2014-12-06 Paper.tex
Prices *COPY, EXP.

\title{Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept VI}}}
\author{
    Dr. Gavin Wood\\
    Co-Founder \& Lead, Ethereum Project\\
    gavin@ethereum.org
}
\begin{document}

@@

\begin{eqnarray}
C(\boldsymbol{\sigma}, \boldsymbol{\mu}, I) & \equiv & G_{memory}(\boldsymbol{\mu}'_i - \boldsymbol{\mu}_i) + \begin{cases}
C_\text{\tiny SSTORE}(\boldsymbol{\sigma}, \boldsymbol{\mu}) & \text{if} \quad w = \text{\small SSTORE} \\
G_{call} + \boldsymbol{\mu}_\mathbf{s}[0] & \text{if} \quad w = \text{\small CALL}\\
G_{create} & \text{if} \quad w = \text{\small CREATE}\\
G_{sha3} & \text{if} \quad w = \text{\small SHA3}\\
G_{sload} & \text{if} \quad w = \text{\small SLOAD}\\
G_{balance} & \text{if} \quad w = \text{\small BALANCE}\\
G_{stop} & \text{if} \quad w = \text{\small STOP}\\
G_{suicide} & \text{if} \quad w = \text{\small SUICIDE}\\
G_{step} & \text{otherwise}
\end{cases} \\
w & \equiv & \begin{cases} I_\mathbf{b}[\boldsymbol{\mu}_{pc}] & \text{if} \quad \boldsymbol{\mu}_{pc} < \lVert I_\mathbf{b} \rVert \\
\text{\small STOP} & \text{otherwise}
\end{cases}
\end{eqnarray}

where $C_\text{\tiny SSTORE}$ is specified in the appropriate section below. Note the memory cost component, given as the product of $G_{memory}$ and the maximum of 0 and the ceiling of the number of words in size that the memory must be over the current number of words, $\boldsymbol{\mu}_i$ in order that all accesses reference valid memory whether for read or write. Such accesses must be for non-zero number of bytes. Referencing a zero length range (e.g. by attempting to pass it as the input range to a CALL) does not require memory to be extended to the beginning of the range. $\boldsymbol{\mu}'_i$ is defined as this new maximum number of words of active memory; special-cases are given where these two are not equal.

>>>>

\title{Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - WiP}}}
\author{
    Dr. Gavin Wood\\
    Co-Founder \& Lead, Ethereum Project\\
    gavin@ethereum.org
}
\begin{document}

@@

\begin{eqnarray}
C(\boldsymbol{\sigma}, \boldsymbol{\mu}, I) & \equiv & G_{memory}(\boldsymbol{\mu}'_i - \boldsymbol{\mu}_i) + \begin{cases}
C_\text{\tiny SSTORE}(\boldsymbol{\sigma}, \boldsymbol{\mu}) & \text{if} \quad w = \text{\small SSTORE} \\
C_\text{\tiny EXP}(\boldsymbol{\mu}) & \text{if} \quad w = \text{\small EXP} \\
G_{step} + G_{copy}\times\boldsymbol{\mu}_\mathbf{s}[2] & \text{if} \quad w = \text{\small CALLDATACOPY} \\
G_{step} + G_{copy}\times\boldsymbol{\mu}_\mathbf{s}[2] & \text{if} \quad w = \text{\small CODECOPY} \\
G_{step} + G_{copy}\times\boldsymbol{\mu}_\mathbf{s}[3] & \text{if} \quad w = \text{\small EXTCODECOPY} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_\mathbf{s}[1] & \text{if} \quad w = \text{\small LOG0} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_\mathbf{s}[1]+G_{logtopic} & \text{if} \quad w = \text{\small LOG1} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_\mathbf{s}[1]+2G_{logtopic} & \text{if} \quad w = \text{\small LOG2} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_\mathbf{s}[1]+3G_{logtopic} & \text{if} \quad w = \text{\small LOG3} \\
G_{log}+G_{logdata}\times\boldsymbol{\mu}_\mathbf{s}[1]+4G_{logtopic} & \text{if} \quad w = \text{\small LOG4} \\
G_{call} + \boldsymbol{\mu}_\mathbf{s}[0] & \text{if} \quad w = \text{\small CALL}\\
G_{create} & \text{if} \quad w = \text{\small CREATE}\\
G_{sha3} & \text{if} \quad w = \text{\small SHA3}\\
G_{sload} & \text{if} \quad w = \text{\small SLOAD}\\
G_{balance} & \text{if} \quad w = \text{\small BALANCE}\\
G_{stop} & \text{if} \quad w = \text{\small STOP}\\
G_{suicide} & \text{if} \quad w = \text{\small SUICIDE}\\
G_{step} & \text{otherwise}
\end{cases} \\
w & \equiv & \begin{cases} I_\mathbf{b}[\boldsymbol{\mu}_{pc}] & \text{if} \quad \boldsymbol{\mu}_{pc} < \lVert I_\mathbf{b} \rVert \\
\text{\small STOP} & \text{otherwise}
\end{cases}
\end{eqnarray}

where $C_\text{\tiny SSTORE}$ is specified in the appropriate section below. Note the memory cost component, given as the product of $G_{memory}$ and the maximum of 0 \& the ceiling of the number of words in size that the memory must be over the current number of words, $\boldsymbol{\mu}_i$ in order that all accesses reference valid memory whether for read or write. Such accesses must be for non-zero number of bytes. Referencing a zero length range (e.g. by attempting to pass it as the input range to a CALL) does not require memory to be extended to the beginning of the range. $\boldsymbol{\mu}'_i$ is defined as this new maximum number of words of active memory; special-cases are given where these two are not equal.
